---
title: "Prediction Assignment Writeup"
author: "Jia Jing Liew"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE)
```

Loading Data
···{r}
setwd("~/Course2 Assignment 8")
install.packages("caret",dependencies=FALSE)
require(caret)
require(dplyr)
require(data.table)
require(randomForest)
require(knitr)
traininglink<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testinglink<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(traininglink, destfile="pml-training.csv", method = "curl")
download.file(testinglink, destfile="pml-testing.csv", method = "curl")

atrain<-tbl_df(fread("pml-training.csv",na.strings=c('#DIV/0!', '', 'NA')))
atest<-tbl_df(fread("pml-testing.csv",na.strings=c('#DIV/0!', '', 'NA')))
```

Spliting Data In Train And Test Part Which In 70% And 30%, Respectively
```{r}
set.seed(1800)
atrain1 <- createDataPartion(y=atrain$classe, p = 0.7, list = FALSE)
actual.atraining <- atrain[atrain1,]
actual.atesting <- atrain[-atrain1,]
```

Prepare The Model Of The Data
```{r}
nzv<-nearZeroVar(actual.atraining)
actual.atraining <- actual.atraining[,-nzv]
actual.atesting <- actual.atesting[,-nzv]

mostlyNA <- sapply(actual.atraining,function(x) mean(is.na(x))) > 0.95
actual.atraining<-actual.atraining[,mostlyNA==FALSE]
actual.atesting<-actual.atesting[,mostlyNA==FALSE]

actual.atraining <- actual.atraining[,-(1:5)]
actual.atesting <- actual.atesting[,-(1:5)]
```

Starting Build Model And Predicting The Results Via The Model
```{r}
set.seed(1800)
ct1<-trainControl(method="cv",number=3)
modelRF  <- train( classe ~.,data = actual.atraining,method = "rf",trControl = ct1 )

set.seed(1800)
ct2<-trainControl(method="repeatedcv",number = 5,repeats = 1)
modelBM <- train( classe ~.,data = actual.atraining,method = "gbm",trControl = ct2,verbose = FALSE)

prediction.test.rf <- predict(modelRF,actual.atesting)
conf.matrix.rf <- confusionMatrix(prediction.test.rf,as.factor(actual.atesting$classe))
conf.matrix.rf
dim(conf.matrix.rf)


prediction.test.bm<- predict(modelBM,actual.atesting)
conf.matrix.bm<-confusionMatrix(prediction.test.rf,as.factor(actual.atesting$classe))
conf.matrix.bm
dim(conf.matrix.bm)
```

Investigating And Ploting Some Diagrams 
```{r}
summary(modelRF)
summary(modelBM)


qplot(num_window,roll_belt, data = actual.atraining, col = classe)
qplot(num_window, pitch_forearm, data = actual.atraining, col = classe)
qplot(roll_belt, pitch_forearm, data = actual.atraining, col = classe)
```